Elephant Seal Age JAE Intraspecific Variation

### 2023-12-07 paper/paperv3.qmd
Add details for pup sex

```{r}
#| label: fig-sex_ratio
#| fig-cap: "Pup sex skews slightly towards males with increasing maternal age, but it's not significant."
#| fig-width: 4.5
#A: Pup sex shifts towards males with increasing maternal age, but it's not significant.

@@

@@

pup_sex_data %>% 
  group_by(age, pupsex) %>%
  summarize(n = n(), .groups = "drop") %>% 
  pivot_wider(values_from = n, names_from = pupsex) %>% 
  mutate(num = M + F,
         percm = M / num,
         se = (percm * (1 - percm) / num)^0.5) %>% 
  ggplot(aes(x = age, y = percm)) +
  geom_hline(yintercept = 0.5, color = "gray75", linetype = "dashed") +
  geom_ribbon(aes(ymin = percm_lwr, ymax = percm_upr), 
              pup_sex_pred,
              fill = "#829BD1",
              alpha = 0.25) + 
  geom_line(data = pup_sex_pred, 
            color = "#829BD1", 
            linewidth = 1) + 
  geom_pointrange(aes(ymin = percm - se, ymax = percm + se), 
                  size = 0.25) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  labs(x = "Maternal Age (Years)", y = "% Male Pups (Mean ± SE)") +
  theme_few() + 
  theme(axis.title = element_text(size = 13))

@@

>>>>

```{r}
#| label: fig-sex_ratio
#| fig-cap: !expr "str_glue('Offspring sex ratio skews towards males with increasing maternal age (p = {format_pval(summary(pup_sex_mod)$coefficients[\"age\", \"Pr(>|z|)\"] / 2, 3)}). Mothers aged 12, 13, and 17 gave birth to significantly more male than female offspring (red stars).')"
#| fig-width: 4.5

@@

pup_sex_summary <- pup_sex_data %>% 
  group_by(age, pupsex) %>%
  summarize(n = n(), .groups = "drop") %>% 
  pivot_wider(values_from = n, names_from = pupsex) %>% 
  mutate(num = M + F,
         percm = M / num,
         se = (percm * (1 - percm) / num)^0.5,
         pval = map2_dbl(M, num, \(x, n) binom.test(x, n, alternative = "greater")$p.value))

signif_male <- filter(pup_sex_summary, pval < 0.05)

@@

ggplot(pup_sex_summary, aes(x = age, y = percm)) +
  geom_hline(yintercept = 0.5, color = "gray75", linetype = "dashed") +
  geom_ribbon(aes(ymin = percm_lwr, ymax = percm_upr), 
              pup_sex_pred,
              fill = "#829BD1",
              alpha = 0.25) + 
  geom_line(data = pup_sex_pred, 
            color = "#829BD1", 
            linewidth = 1) + 
  geom_pointrange(aes(ymin = percm - se, ymax = percm + se), 
                  size = 0.25) +
  geom_point(aes(y = percm + se + 0.05),
             signif_male,
             shape = 8,
             color = "firebrick") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  labs(x = "Maternal Age (Years)", y = "% Male Pups (Mean ± SE)") +
  theme_few() + 
  theme(axis.title = element_text(size = 13))

@@

Supplemental table for sex ratios

```{r}
#| label: tbl-pup-sex
#| tbl-cap: "Offspring sex ratio skewed towards males with increasing maternal age. Mothers age 12, 13, and 17 gave birth to significantly more male than female pups (bold)."

pup_sex_tbl <- pup_sex_summary %>% 
  transmute(
    Age = age,
    `Male pups` = M,
    `Total pups` = num,
    `% male` = scales::label_percent(accuracy = 0.1)(percm),
    `p value` = format_pval(pval, 3)
  )

is_signif <- which(pup_sex_tbl$`p value` < "0.05")

knitr::kable(pup_sex_tbl) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(is_signif, bold = TRUE)
```
